The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-07-01 borel-regularity.tex
Drop draft text from Laplace-Borel basics section
Also, correct a typo.

%\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}

%The Borel transform on $T^*B_{\zeta = 0}$ is the $\C$-linear map
%\begin{align*}
%\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}.
%\end{align*}
%In general, by linearity,
%\begin{align*}
%\borel_\zeta\big[a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
%\end{align*}
% \textcolor{PaleVioletRed}{[I cannot  quite see what this paragraph is doing.]} If a function $\varphi$ belongs to $\singexpalg{0}(\Omega)$, and its Taylor series
% \[ \series{\varphi} = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots \]
% has an infinite radius of convergence, then the Taylor coefficients decay fast enough for us to take the Laplace transform term by term~\cite[Theorem 5.20]{diverg-resurg-i}:
% \begin{align*}
%   \laplace_{\zeta, 0}\varphi&=\laplace_{\zeta,0}\left[\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}\right]\\
%   &=\sum_{n=0}^\infty a_{n+1}\,\laplace_{\zeta,0}\left[\frac{\zeta^n}{n!}\right]\\
%   &=\sum_{n=0}^\infty a_{n+1}z^{-n-1}
% \end{align*}
% As a result, we can recover the Taylor series $\series{\varphi}$ from the series
% \[ \series{\Phi} = a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \]
% using the Borel transform:
% \begin{align*}
% \borel_\zeta \series{\Phi}&=\borel_\zeta\left[\sum_{n=0}^\infty a_{n+1}z^{-n-1}\right]\\
% &=\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}.
% \end{align*}
% We took the Borel transform with respect to the coordinate $\zeta$ because $\series{\Phi}$ represents a holomorphic function on the cotangent space $T^*_{\zeta = 0}B$.

On a different fiber of $T_{\zeta=\alpha}^*B$, the Borel transform $\borel_{\zeta_\alpha}$ in the translated coordinate $\zeta_\alpha$ is defined on monomials as the inverse of the Laplace transform $\laplace_{\zeta_\alpha,0}$
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
 \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta_\alpha}} \\ \{1, \zeta_\alpha, \frac{1}{2!} \zeta_\alpha^2, \frac{1}{3!} \zeta_\alpha^3, \ldots\} \arrow{u}{\laplace_{\zeta_\alpha, 0}}
\end{tikzcd}
\end{center}
It extends countable linearity to a map $\borel_{\zeta_\alpha} \maps z^{-1} \C \llbracket z^{-1} \rrbracket  \to \C \llbracket \zeta_\alpha \rrbracket$.
%\begin{align*}
%\borel_{\zeta_b} \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C %\llbracket \zeta_b \rrbracket \\
%\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta_b^n}{n!},
%\end{align*}
%%\begin{align*}
 %%    \borel_{\zeta_b}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_b \rrbracket  \\
  %%   z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
 %%\end{align*}
%we could again recover ${\varphi}_b$.

%Summarizing, we can describe the geometry of Borel and Laplace transforms by drawing the following diagram
%\begin{center}
%\begin{tikzcd}[every arrow/.append style={shift left}]
 %\text{functions on } T^*_{\zeta=0}B \arrow{d}{\borel_{\zeta}} & & \text{functions on } T^*_{\zeta=b}B \arrow{d}{\borel_{\zeta_b}}\arrow[ll,swap,"\mathsf{T}_b^*"] \\ 
 %\text{functions of } \zeta \arrow{u}{\laplace_{\zeta, 0}}\arrow[rr,"\mathsf{T}_b"'] & & \text{functions of } \zeta_b \arrow{u}{\laplace_{\zeta_b, 0}}
%\end{tikzcd}
%\end{center}
%where $\mathsf{T}_b$ denotes the translation map $\mathsf{T}_b(\zeta)=\zeta_b$. \textcolor{orange}{I don't like much the word function and the map $\mathsf{T}_b$, but we could change later.}

%%It's also possible to recover the definition of $\mathcal{B}_{\zeta,\alpha}$ from the properties of $\laplace_{\zeta_\alpha,0}$, as discussed in Section~\ref{transl-borel}.

%%%We then could've recovered the Taylor series of $\varphi$ using the Borel transform on $T^*B_{\zeta = \alpha}$, which is defined as
%%%\begin{align*}
%%%\borel_{\zeta_\alpha} \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta_\alpha \rrbracket \\
%%z^{-n-1} & \mapsto \frac{\zeta_\alpha^n}{n!}.
%%\end{align*}

%%%working in a different cotangent space $T^*B_{\zeta = \alpha}$, we'd take the Borel transform with respect to $\zeta_\alpha$ instead, as described in Section~\ref{transl-borel}.

%\color{Peru}
%\textbf{[Draft version]} The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$. More precisely, $\borel_\zeta$ is a $\C$-linear map 
%\begin{align*}
%\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
%1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
%\end{align*}
%where $\delta$ is a ``convolution unit'', namely $\phi\ast \delta= \delta\ast \phi= \phi$ (see convolution below \textcolor{magenta}{[add convolution]}).

%%It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
%\begin{align*}
 %   \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\mathcal{J}_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\mathcal{J}_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
  %  &=\sum_{n=0}^{\infty}a_n \frac{\zeta^n}{n!}
%\end{align*}
%where in the second step we formally interchange the integral and the sum. 
%\color{black}
\subsubsection{Action on trans-monomials}\label{sec:action_transseries}
%Recall from the discussion in Section~\ref{sec:history_ODE}, that formal solutions of irregular singualr ODEs are in form of trans-monomials. 
%%
%%{\em Trans-series} are formal objects that greatly generalize formal power series. Their full definition is quite involved, especially when complex exponents are allowed~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}. We will only see examples of the simple form 
%%\[  e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha, \]
%%where $\alpha$ is a complex number, each $\sigma_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$. This is an example of a {\em trans-monomial}.
%%
%%Trans-monomials of this form play a crucial role in the theory of ODEs with irregular singularities. Linear combinations of such trans-monomials encode the Stokes phenomenon:
%%
%%In particular, they exhibit a formal analogue of the Stokes phenomenon: their asymptotics can change sharply from one direction to the next. Trans-monomials $e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha$ can be ordered by $\Re(e^{i\theta} \alpha)$ for any direction $\theta$. When a trans-monomial \textcolor{orange}{[of this form]} converges, its sum becomes dominated by the lowest term in this ordering as $\Re(e^{-i\theta} z)$ grows.
%%\[\sum_{\alpha\in A}  e^{\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha \]
%%$A$ is the set of roots of $P$.

We can extend the definition of the Borel transform to these trans-monomials by recognizing that $\laplace_{\zeta, \alpha}$ sends ordinary monomials to trans-monomials, and then taking advantage of the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ given by identity~\eqref{change-chart}.
\begin{definition}
On each ordinary monomial within a trans-monomial, $\borel_\zeta$ acts as the formal inverse of $\laplace_{\zeta,\alpha}$:
\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-n-1} \big]=e^{-\alpha z} z^{-n-1}. \]
The action of $\borel_\zeta$ extends to all of $e^{-\alpha z} \C\llbracket z^{-1} \rrbracket$ by countable linearity.
\end{definition}
From this definition, and identity~\eqref{change-chart}, we deduce that
\begin{align*}
e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = e^{-z\alpha} z^{-n-1} \\
\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = z^{-n-1} \\
\borel_{\zeta}\big[e^{-\alpha z}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}.
\end{align*}
%%%and taking the inverse of $\laplace_{\zeta_\alpha,0}$ we find
%Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}). 
%
%We extend the Borel transform to transseries, defining \[\borel_\zeta \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta_\alpha \rrbracket\] as the formal inverse of $\laplace_{\zeta, \alpha}$. To be more precise, we define the action on trans-monomial so that the diagram
%%\begin{center}
%%\begin{tikzcd}
%%& e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \arrow[rd, "\borel_\zeta"] \\
%%\C\llbracket \zeta \rrbracket \arrow[ru, "\laplace_{\zeta, \alpha}"] \arrow[rr, "\text{change of variable}"'] & & \C\llbracket \zeta_\alpha \rrbracket
%%\end{tikzcd}
%%\end{center}
%\begin{lemma}
%%%\[\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big]=\frac{\zeta_\alpha^n}{n!}.\]
In other words, the diagram 
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd,"\borel_\zeta"'] \arrow[rr,"e^{-z\alpha}"]& & e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd, "\borel_\zeta"] \\
& & \\
\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "\mathsf{T}_{-\alpha}^*"'] & & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}\arrow[lluu,"\laplace_{\zeta_\alpha, 0}" description]\arrow{uu}{\laplace_{\zeta, \alpha}}
\end{tikzcd}
\end{center}
commutes, where $\mathsf{T}_{-\alpha}$ denotes traslation by $-\alpha$. Notice that $\laplace_{\zeta, 0}$ and $\laplace_{\zeta, \alpha}$ produce functions on the fiber $T^*_{\zeta = 0}B$, while $\laplace_{\zeta_\alpha, 0}$ produces functions on the fiber $T^*_{\zeta = \alpha}B$, so this argument depends on the fact that $z$ is defined almost globally $T^*B$.
%\end{lemma}

@@

 %Therefore, we learn that $\borel_{\zeta_\alpha}$ is a $\C$-linear map from formal power series in the frequency variable $z$ to formal power series in the position variable $\zeta_\alpha$, it is defined by 
 %\begin{align*}
    % \borel_{\zeta_\alpha}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_\alpha \rrbracket  \\
    % z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
 %\end{align*}
%\textcolor{orange}{[Move to beginning?]} Furthermore, we learn that the action of $\borel_{\zeta_\alpha}$ extends to trans-monomials: $\borel_{\zeta_\alpha}\colon e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta  \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.

@@

%&=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{j-1}}{(j-1)!}\ast\frac{\zeta^{n-j-1}}{(n-j-1)!}\\
%&= a_0b_0\delta + \sum_{n=1}^\infty\sum_{j=0}^na_jb_{n-j}   \left( \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\right)\ast\left(\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\right)
% Notice that if $z$ is the coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n-1}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n-1}$, then the convolution product of $\series{\phi}:=\borel_\zeta\series{\Phi}$ and $\series{\psi}:=\borel_\zeta\series{\Psi}$ is 
%  \[\series{\psi}\ast\series{\phi}=\borel_\zeta(\series{\Psi}\series{\Phi}).\]
%  Hence, if $z$ denotes a coordinate on $T^*_{\zeta=0}B$, the Borel transform $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, and $\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
% Furthermore, since $\series{\phi},\series{\psi}\in\C\{\zeta\}$ are convergent formal series, it follows that the sum of $\series{\psi}\ast\series{\phi}$ is the convolution $\hat{\psi}\ast\hat{\phi}$, where $\hat{\phi},\hat{\psi}$ are the sums of $\series{\phi}, \series{\psi}$ respectively. 
% \end{definition}

@@

% Equivalntly, $1$-Gevrey series are caracterized as follows:
% \begin{lemma}
% Let $\series{\Phi}\in\C \llbracket z^{-1} \rrbracket$. Then, $\series{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel_\zeta\series{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions. 
% \end{lemma}
%     If $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$, and $\series{\Phi}(z)=\sum_{n=0}^\infty a_n z^{-n-1}$, then by definition, there exixst a constant $A>0$ such that $|a_n|\lesssim A^n n!$ for all $n\ge 0$. Therefore,
%     \[\borel_\zeta\series{\Phi}=\sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\]
%     which has finite radius of convergence $A^{-1}$. 
%     Conversely, if $\borel_\zeta\series{\Phi}$ is a germ of analytic functions, i.e. $\borel_\zeta\series{\Phi}=\sum_{n=0}^\infty a_n \zeta^n$ has finte radius of convergence $1/A$, for some constant $A>0$, then the formal Laplace transform of $\borel_\zeta\series{\Phi}$ gives 
%     \[\sum_{n=0}^\infty a_n\, n!\, z^{-n-1}\]
%     and $|a_n n!|\le |a_n| n!\lesssim A^n n!$. 
The space of $1$-Gevrey series is close under the Cauchy product. In addition, 
\[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket_1\to\C\delta + \C\{\zeta\}\]
extends to an algebra homomorphism, where $\C\{\zeta\}$ is endowed with the convolution product defined in Definition~\ref{def:convolution_formal}. 
% \begin{definition}{(see \cite[Definition 5.12]{diverg-resurg-i})}
%     Let $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$, and $z$ be a coordinate on the cotangent fiber over $\zeta=0$. Then, the convolution product of $\series{\phi}:=\borel_\zeta\series{\Phi}$ and $\series{\psi}:=\borel_\zeta\series{\Psi}$ is defined as
% \[\borel_\zeta(\series{\Psi}\series{\Phi})=:\series{\psi}\ast\series{\phi}.\]
% Furthermore, since $\series{\phi},\series{\psi}\in\C\{\zeta\}$ are convergent formal series, it follows that the sum of $\series{\psi}\ast\series{\phi}$ is the convolution $\hat{\psi}\ast\hat{\phi}$, where $\hat{\phi},\hat{\psi}$ are the sums of $\series{\phi}, \series{\psi}$ respectively. 
% \end{definition}
% The definition of convolution product for germs of holomorphic functions at $\zeta=0$, can be generalized to germs of analytic functions at $\zeta=\alpha$, using the Borel transform $\borel_{\zeta_\alpha}$ on $1$-Gevrey series on the fiber over $\zeta=\alpha$. 
% \begin{definition}
%     Let $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$, and $z$ be a coordinate on the cotangent fiber over $\zeta=\alpha$. Then, the convolution product of $\series{\phi}:=\borel_{\zeta_\alpha}\series{\Phi}$ and $\series{\psi}:=\borel_{\zeta_\alpha}\series{\Psi}$ is defined as
% \[\borel_{\zeta_\alpha}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_{\zeta_\alpha,0}\series{\phi}.\]
% Furthermore, the sum of $\series{\psi}\ast_{\zeta_\alpha,0}\series{\phi}$ is the convolution $\hat{\psi}\ast_{\zeta_\alpha,0}\hat{\phi}$. 
% \end{definition}
In fact, we deduce that the Borel transform induces an algebra homomorphism on $1$-Gevrey series. Similarly, if $z$ is coordinate on the fiber over $\zeta=\alpha$, the Borel transform $\borel_{\zeta_\alpha}$ induces an isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ edowed with the Cauchy product, and $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution $\ast_{\zeta_\alpha,0}$.  
%     Let $z$ be a coordinate on $T^*_{\zeta=\alpha}B$. The Borel transform $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket_1$ to $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$. 
\subsubsection{Compatibility of the convolution product with the geometry}\label{sec:convolution-compatible}
The convolution product is compatible with the change of translation chart: if $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=b}B$ and let $\series{\psi}:=\borel_{\zeta_b}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_b}\series{\Phi}$
\[\borel_{\zeta_b}(\series{\Psi}\series{\Phi})=\hat{\psi}\ast \hat{\phi}=\int_{0}^{\zeta_b}\hat{\psi}(\zeta_b-\zeta')\hat{\phi}(\zeta')d\zeta'\]
Furthermore, we can extend the previous definition to trans-series: let $\series{\Phi}, \series{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=0} B$, we define \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}.\]
Then the sum of $\series{\psi}\ast_\alpha\series{\phi}$ can be explicitly written as 
    \hat{\psi}\ast_\alpha\hat{\phi}=\int_\alpha^{\zeta}d\zeta' \hat{\psi}(\zeta-\zeta')\hat{\phi}(\zeta')
where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\series{\phi}$ and $\series{\psi}$ in a neighbourhood of $\zeta=\alpha$.

@@

We first assume $\Phi=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, and assume $z$ is a function on $T^*_{\zeta=0}B$. Then, for every $\lambda\in (-1,\infty)$
\begin{align*}
    \borel_\zeta(z^{-\lambda}{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)&=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^\zeta (\zeta-t)^{\lambda-1}\phi(t)dt=\borel_\zeta (z^{-\lambda})\ast_\alpha\phi
\end{align*}
where we use the identity $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, that generalizes properties $(i)$ and $(ii)$ in Proposition~\ref{prop:L-int-op}. Hence \[\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\big[\borel_\zeta\Phi\big].\]
%However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
Then, we study the case when $\Phi$ and $z$ are functions on the fiber over $\zeta=b$, and we assume $\Phi=\laplace_{\zeta_b,0}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_b)$. For every $\lambda\in (-1,\infty)$
\begin{multline*}
    \borel_{\zeta_b}\big[z^{-\lambda}\Phi\big]=\borel_{\zeta_b}\big[z^{-\lambda}\laplace_{\zeta_b,0}\phi\big]=\borel_{\zeta_b}\big[\laplace_{\zeta_b,0}\partial_{\zeta_b,0}^{-\lambda}\phi\big]=\partial_{\zeta_b,0}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_b} (\zeta_b-t)^{\lambda-1}\phi(t)dt\\
    =\borel_{\zeta_b}(z^{-\lambda})\ast\phi
\end{multline*}
hence,  \[\partial_{\zeta_b,0}^{-\lambda}\big[\borel_{\zeta_b}\Phi\big]=\borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}{\Phi}.\]
\end{remark}
\end{verify}
%

>>>>

On a different fiber of $T_{\zeta=\alpha}^*B$, the Borel transform $\borel_{\zeta_\alpha}$ in the translated coordinate $\zeta_\alpha$ is defined on monomials as the inverse of the Laplace transform $\laplace_{\zeta_\alpha,0}$
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
 \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta_\alpha}} \\ \{1, \zeta_\alpha, \frac{1}{2!} \zeta_\alpha^2, \frac{1}{3!} \zeta_\alpha^3, \ldots\} \arrow{u}{\laplace_{\zeta_\alpha, 0}}
\end{tikzcd}
\end{center}
It extends countable linearity to a map $\borel_{\zeta_\alpha} \maps z^{-1} \C \llbracket z^{-1} \rrbracket  \to \C \llbracket \zeta_\alpha \rrbracket$.
%
\subsubsection{Action on trans-monomials}\label{sec:action_transseries}
%
We can extend the definition of the Borel transform to these trans-monomials by recognizing that $\laplace_{\zeta, \alpha}$ sends ordinary monomials to trans-monomials, and then taking advantage of the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ given by identity~\eqref{change-chart}.
\begin{definition}
On each ordinary monomial within a trans-monomial, $\borel_\zeta$ acts as the formal inverse of $\laplace_{\zeta,\alpha}$:
\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-n-1} \big]=e^{-\alpha z} z^{-n-1}. \]
The action of $\borel_\zeta$ extends to all of $e^{-\alpha z} \C\llbracket z^{-1} \rrbracket$ by countable linearity.
\end{definition}
From this definition, and identity~\eqref{change-chart}, we deduce that
\begin{align*}
e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = e^{-z\alpha} z^{-n-1} \\
\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = z^{-n-1} \\
\borel_{\zeta}\big[e^{-\alpha z}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}.
\end{align*}
In other words, the diagram 
\begin{center}
\begin{tikzcd}[every arrow/.append style={shift left}]
\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd,"\borel_\zeta"'] \arrow[rr,"e^{-z\alpha}"]& & e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd, "\borel_\zeta"] \\
& & \\
\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "\mathsf{T}_{-\alpha}^*"'] & & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}\arrow[lluu,"\laplace_{\zeta_\alpha, 0}" description]\arrow{uu}{\laplace_{\zeta, \alpha}}
\end{tikzcd}
\end{center}
commutes, where $\mathsf{T}_{-\alpha}$ denotes traslation by $-\alpha$. Notice that $\laplace_{\zeta, 0}$ and $\laplace_{\zeta, \alpha}$ produce functions on the fiber $T^*_{\zeta = 0}B$, while $\laplace_{\zeta_\alpha, 0}$ produces functions on the fiber $T^*_{\zeta = \alpha}B$, so this argument depends on the fact that $z$ is defined almost globally $T^*B$.

@@

@@

@@

The space of $1$-Gevrey series is closed under the Cauchy product. In addition, 
\[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket_1\to\C\delta + \C\{\zeta\}\]
extends to an algebra homomorphism, where $\C\{\zeta\}$ is endowed with the convolution product defined in Definition~\ref{def:convolution_formal}. In fact, we deduce that the Borel transform induces an algebra homomorphism on $1$-Gevrey series. Similarly, if $z$ is coordinate on the fiber over $\zeta=\alpha$, the Borel transform $\borel_{\zeta_\alpha}$ induces an isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ edowed with the Cauchy product, and $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution $\ast_{\zeta_\alpha,0}$.
\begin{verify}
\subsubsection{Compatibility of the convolution product with the geometry}\label{sec:convolution-compatible}
The convolution product is compatible with the change of translation chart: if $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=b}B$ and let $\series{\psi}:=\borel_{\zeta_b}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_b}\series{\Phi}$
\[\borel_{\zeta_b}(\series{\Psi}\series{\Phi})=\hat{\psi}\ast \hat{\phi}=\int_{0}^{\zeta_b}\hat{\psi}(\zeta_b-\zeta')\hat{\phi}(\zeta')d\zeta'\]
Furthermore, we can extend the previous definition to trans-series: let $\series{\Phi}, \series{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=0} B$, we define \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}.\]
Then the sum of $\series{\psi}\ast_\alpha\series{\phi}$ can be explicitly written as 
\begin{equation}
    \hat{\psi}\ast_\alpha\hat{\phi}=\int_\alpha^{\zeta}d\zeta' \hat{\psi}(\zeta-\zeta')\hat{\phi}(\zeta')
\end{equation}
where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\series{\phi}$ and $\series{\psi}$ in a neighbourhood of $\zeta=\alpha$.

@@

We first assume $\Phi=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, and assume $z$ is a function on $T^*_{\zeta=0}B$. Then, for every $\lambda\in (-1,\infty)$
\begin{align*}
    \borel_\zeta(z^{-\lambda}{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)&=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^\zeta (\zeta-t)^{\lambda-1}\phi(t)dt=\borel_\zeta (z^{-\lambda})\ast_\alpha\phi
\end{align*}
where we use the identity $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, that generalizes properties $(i)$ and $(ii)$ in Proposition~\ref{prop:L-int-op}. Hence \[\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\big[\borel_\zeta\Phi\big].\]
%However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
Then, we study the case when $\Phi$ and $z$ are functions on the fiber over $\zeta=b$, and we assume $\Phi=\laplace_{\zeta_b,0}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_b)$. For every $\lambda\in (-1,\infty)$
\begin{multline*}
    \borel_{\zeta_b}\big[z^{-\lambda}\Phi\big]=\borel_{\zeta_b}\big[z^{-\lambda}\laplace_{\zeta_b,0}\phi\big]=\borel_{\zeta_b}\big[\laplace_{\zeta_b,0}\partial_{\zeta_b,0}^{-\lambda}\phi\big]=\partial_{\zeta_b,0}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_b} (\zeta_b-t)^{\lambda-1}\phi(t)dt\\
    =\borel_{\zeta_b}(z^{-\lambda})\ast\phi
\end{multline*}
hence,  \[\partial_{\zeta_b,0}^{-\lambda}\big[\borel_{\zeta_b}\Phi\big]=\borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}{\Phi}.\]
\end{remark}
\end{verify}
%
\subsubsection{Analytic to formal}
%
Consider an open set $\Omega \subset \C$ that touches but does not contain $\zeta = 0$. The spaces $\singexp{\sigma}{\Lambda}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}. To study Borel summation, however, we also need to take shifted Taylor expansions around $\zeta = 0$, turning holomorphic functions $\phi \in \singexp{\sigma}{\Lambda}(\Omega)$ into convergent power series $\series{\phi} \in \zeta^\rho \C\{\zeta\}$ with $\rho \ge \sigma$. The following discussion, leading up to Lemma~\ref{lem:shifted_holo_closed}, will help us stay within a subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the shifted Taylor series exists.
